---
title: "R Notebook"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---


```{r}
library(magrittr)
library(dplyr)
library(readr)
library(lubridate)
library(leaflet)
library(ggplot2)
library(sf)
library(tidyverse)
```

```{r}
df <- read_csv("Downloads/StructureMovementPermits_csv.csv")
n_distinct(df$`Original Address 1`)
df <- df[order(df[["Issued Date"]], decreasing = TRUE), ]
df <- df[!duplicated(df$`Original Address 1`), ]
df <- df[!grepl("ADU", df$Description),]
df <- filter(df, `Issued Date` > '2004-01-01')
```


This is the total number of permits issued (1548).
```{r}
nrow(df)
```

This is the # of permits by year 

```{r}
df %>%
mutate(year = format(`Issued Date`, "%Y")) %>%
group_by(year) %>%
summarise(count = n_distinct(`Original Address 1`))
```
This is the # of permits by year and by Zip Code, in order of frequency
```{r}
cross <- df %>%
mutate(year = format(`Issued Date`, "%Y")) %>%
group_by(year, `Original Zip`) %>%
summarise(count = n_distinct(`Original Address 1`))

cross[order(-cross$count),]

```


This is the # of permits by Zip Code, in order of frequency
```{r}
zip <- df %>%
group_by(`Original Zip`) %>%
summarise(count = n_distinct(`Original Address 1`))

zip[order(-zip$count),]

```

This is the # of permits by Council District, in order of frequency
```{r}
council <- df %>%
group_by(`Council District`) %>%
summarise(count = n_distinct(`Original Address 1`))

council[order(-council$count),]
```
This is the # of permits by Contractor, in order of frequency
```{r}
contractor <- df %>%
group_by(`Contractor Company Name`) %>%
summarise(count = n_distinct(`Original Address 1`))

contractor[order(-contractor$count),]
```


Creating a new column of complete addresses
```{r}
df$Combined<-paste(df$`Original Address 1`,df$`Original City`,sep=",")
df$Combined <- paste(df$Combined, df$`Original State`,sep=",")
df$Combined <- paste(df$Combined, df$`Original Zip`,sep=",")
```


Map of Different Addresses
```{r}
library(ggmap)
library(tidygeocoder)
library(mapview)
AddressFrequency <- function(addresses){
  tab <- table(addresses)
  unique.points <- data.frame(address=names(tab), frequency = c(tab))
  rownames(unique.points) <- NULL
  unique.points
}
freq <- AddressFrequency(df$Combined)
freq <- cbind(freq, geocode(freq, address = address))

newfreq <- na.omit(freq)


mapview(newfreq, xcol = "long", ycol = "lat", crs = 4269, grid = FALSE)

```


